Regime transition identification for basin's governance challenges of water use

### 2020-11-09 tex/main/manuscript.tex
change the title
update abstract in gov.

% PNAS研究论文模板
\templatetype{pnasresearcharticle} % Choose template 
% {pnasresearcharticle} = Template for a two-column research article
% {pnasmathematics} %= Template for a one-column mathematics article
% {pnasinvited} %= Template for a PNAS invited submission
% \usepackage{cite}
\usepackage{url}	
% 文章标题：“流域尺度的水资源利用体系：过渡框架和发展困局”
\title{Regime transition identification for water governance of river basin}
\label{title}
% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
% 作者列表
\author[a, b]{Shuang Song}  % 宋爽，一作
\author[a, b, 1]{Shuai Wang}  % 王老师，通讯
\author[c, d]{Xutong Wu}  % 武旭同
\author[a, b]{Bojie Fu}  % 傅老师
\author[e]{Yongping Wei} % 尉老师

@@

%tag 摘要
\begin{abstract}
	\label{abstract}
	% For water utilization as blood that sustains social developments, humans have harnessed basins, modified river cycles and triggered a range of regime shifts all around the world.
	For sustaining socio-economic development, human have harnessed large rivers and triggered a range of regime shifts at a basin scale all around the world. 
	Detecting these abrupt reorganizations of structure and function is critical to successful future river basin management. 
	Here, considering three main dimensions of water utilization (stress, priority and configuration), we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale to indicate regime shifts. 
	By applying this index to the Yellow River Basin, China, it suggests that there were two regime shifts over half a century, whose drivers were economic growths, managements and efficiency improvement.
	Differ from previous onefold descriptions, IWRU captures various considerations intertwined in water utilization, based on which we proposed a transition framework in interpreting associated changes.
	By identifying and predicting widespread dilemmas in transition of water utilization, this framework can be a useful guideline for big river basins to develop in a coordinated way.
\end{abstract}

>>>>

% PNAS研究论文模板
\templatetype{pnasresearcharticle} % Choose template 
% {pnasresearcharticle} = Template for a two-column research article
% {pnasmathematics} %= Template for a one-column mathematics article
% {pnasinvited} %= Template for a PNAS invited submission
% \usepackage{cite}
\usepackage{url}	
% 文章标题：“流域尺度的水资源利用体系：过渡框架和发展困局”
\title{Regime transition identification for basin's governance challenges of water use}
\label{title}
% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
% 作者列表
\author[a, b]{Shuang Song}  % 宋爽，一作
\author[a, b, 1]{Shuai Wang}  % 王老师，通讯
\author[c, d]{Xutong Wu}  % 武旭同
\author[a, b]{Bojie Fu}  % 傅老师
\author[e]{Yongping Wei} % 尉老师

@@

%tag 摘要
% 为了
\begin{abstract}
	\label{abstract}
	% 为了持续的社会经济发展，人类治理了大型河流，并在世界范围内引发了一系列流域尺度的稳态转换。
	For water uses in sustaining socio-economic development, human have governed large rivers and triggered various regime shifts at a basin scale all around the world. 
	% 由于水治理制度决定谁、何时和如何获得水，因此确定其过渡对于指导有效和可持续的用水至关重要。
	Since water governance regime decides who gets what water, when and how, identification for its changes is critical to guiding effective and sustainable water uses.
	% 在这里，考虑到水治理的三个主要维度(压力、供应和分配)，我们开发了一个流域尺度上的综合水治理指数(IWGI)，以检测制度的变化。
	Here, considering three main dimensions of water governance (stress, provision and allocation), we develop an Integrated Water Governance Index (IWGI) at a basin scale to detect regime shifts.
	% 将该指数应用于中国黄河流域，可以看出，在过去半个多世纪中，有三个政权的转变是由经济增长、管理和效率提高引起的。  
	By applying this index to the Yellow River Basin, China, it suggests there were two regimes shifts of water governance throughout half a century, which were caused by changes of environment, economy and policy.
	% 在此基础上，我们总结了一个与水社会循环相对应的一般制度变迁模式。
	Based on the results, we summarized a widespread regime transition schema, corresponding with trajectories of water uses towards hydro-social cycle.
	% 由于资源挑战和结构挑战主要困扰不同制度下的水治理，这一过渡模式可以作为协调大流域治理的有益指导。
	Since resource challenges and structural challenges mainly bother water governance within different regimes, this schema can be a useful guideline for governing big river basins in a coordinated way.
\end{abstract}
